The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-30 paper/Analisis.tex
Two more paragraphs in off-center emission

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ and 
we moved $0.2 R$ in the x axis.

@@

The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
is shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
they are the most sensitive to rotational velocities. We found that off-center emission 
would generate asymmetric spectra, in particular depending in the location of the 
sphere the double peak would came out with different heights.

\begin{figure}
\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
\caption{Spectra for two off-center spheres
   \label{fig:OCspectra}} 
\end{figure}

@@

... Comparison with Verhamme et al. results on the rotation

@@

>>>>

As we know there is unlikely to find galaxies with radiation sources 
distributed homogeneously. Most of them are in a clumpy distribution 
(Laursen et al 2013*) which affected the resulting spectra. In order 
to study an inhomogeneous distribution we set up a model in which we 
select certain photons that are placed in a specific place but that 
are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
set up, basically we take photons located in a sphere of $0.5 R$ and 
we choose two speheres in each side of the $\hat{\textbf{x}}$ axis
two at $0.25 R$ and the other two at $0.5 R$

@@

The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
is shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
they are the most sensitive to rotational velocities.
\begin{figure}
\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
\caption{Spectra for two off-center spheres
   \label{fig:OCspectra}} 
\end{figure}

There are two new morphological featueres that off-center emission in 
rotating galaxies produces. First in some of our models with especific 
values of velocity and opitcal depth an asymmetry in the peak heights 
is presented, those off-center spheres \textit{(put image reference)} 
located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
present a higher peak in the redshifted part, while those spheres located
at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ where one peak is $20\%$ higher than the other.
This can be apreciated for both set of spheres at $0.25 R$ and $0.5 R$,
 but the effect shows a stronger asymmetry for spheres located at $0.25 R$
 this due to the fact that photons escaping from this spheres goes through 
 a larger hidrogen medium than photons located in the spheres at $0.5 R$.
%poner valores de velocidad y optical depth porcentaje de asimetria

Also for all the off-center models we found that the $Ly\alpha$ line 
width ...

Also for photons located in the spheres at $0.5 R$, we found that for 
some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
the line presents three peaks (blue-shifted, centered, red-shifted). In order to gain a better interpretation of this three peaks trend we run this models with $N_{\gamma} = 10^6$.

@@

... Comparison with Verhamme et al. results on the rotation (Viewing angle)

@@

% BUSCAR asimetrias en observaciones, KUlas, YAMADA  off-center emission
